Real Estate

### 2022-11-08 src/real_estate.Rmd
recalculated rent change

```{r}
# aggregate yardi data into MSAs by cbsa
MSA_realEstate_data <- city_realEstate_data %>% 
  clean_names() %>% 
  group_by(cbsa) %>% 
  # calculate average values for MSAs with more than one city
  summarize(avg_rent_2021 = mean(average_rent_2021, na.rm = TRUE),
            avg_rent_2022 = mean(x2022_rent, na.rm = TRUE),
            avg_occupancy_21 = mean(percent_occupancy_2021, na.rm = TRUE)) %>% 
  # calculate change in rent
  mutate(rent_change21_22 = ((avg_rent_2022- avg_rent_2021)/avg_rent_2021)*100)

>>>>

```{r}
# aggregate yardi data into MSAs by cbsa
MSA_realEstate_data <- city_realEstate_data %>% 
  clean_names() %>% 
   # calculate change in rent
  mutate(rent_change = (x2022_rent - average_rent_2021)/average_rent_2021 * 100) %>% 
  group_by(cbsa) %>% 
  # calculate average values for MSAs with more than one city
  summarize(avg_rent_2021 = mean(average_rent_2021, na.rm = TRUE),
            avg_rent_2022 = mean(x2022_rent, na.rm = TRUE),
            avg_occupancy_21 = mean(percent_occupancy_2021, na.rm = TRUE),
            avg_rent_change = mean(rent_change, na.rm = TRUE))
